### 2020-01-20 methods.tex
updated methods

>>>>

\paragraph{Organization of this paper}

We want to study the effective of Product Norm Metrics in describing trends in the
generalization accuracyof real-word, production quality, pretrained Deep Neural Networks.
In Section \ref{sxn:cv}, we study three well known, and widely available DNN architectures:
the VGG series, the ResNet series, and the DenseNet series of models.  Each have been pretrained
on the full ImageNet dataset\cite{imagenet}, and are distributed with the current of pyTorch (1.4)\cite{pyTorch}.
[Explain more]
